%\documentclass[cprs.tex]{subfiles}

\section*{Instructions for Part 1}
\subsection*{General}

\noindent Together with two other people, they form a group. These people are now also participating in the study here in the BonnEconLab. They don't know who the other two people are. Likewise, the other group members do not know who you are and who the other person is.

\noindent This part consists of 5 rounds.

\subsection*{Decision situation}

As a group, you have a forest. Each group member decides in each round how many trees he/she wants to take from the forest.

\noindent At the beginning of the first round, there are 100 trees in the forest. The maximum number that each group member can take in a round is 7 trees. Each group member makes the decision in each round whether he/she wants to remove 0, 1, 2, 3, 4, 5, 6 or 7 trees.

\noindent This decision will be made at the same time. At the end of each round, each group member receives information about how many trees the entire group has taken, but not how many trees each individual group member has taken.

\subsection*{Development of the forest}

\noindent When trees are removed, the size of the forest initially decreases. At the end of each round, trees can grow back.

\noindent 10\% of the remaining trees grow back. Take e.g. B. that there are 85 trees after the removal. 10\% of this are 8.5 trees, so that a total of 93.5 trees are available at the end of the round. However, they can only cut down completely adult trees.

\noindent In total, the forest can consist of a maximum of 100 trees.

\subsection*{Earnings}

\noindent Each tree taken generates 2 points for the person who took it. For 0 trees removed you get 0 points, for 1 tree removed you get 2 points, for 2 trees removed you get 4 points, etc. If a group member removes 7 trees, he/she receives 14 points at the end of the round.

\noindent In addition to the trees removed, those at the end of the 5th Round remaining trees also points. The value of the forest (2 points per remaining tree) is doubled for this. Then each group member receives an equal share of the value of the forest. Take e.g. B. that 15 trees at the end of the $5^{th}$ Round are available. These 15 trees have a value of 30 points. This value is doubled to 60 points. Each group member now receives an equal share of these 60 points, i.e. 20 points.

\noindent In addition, each group member receives at the beginning of the 1st Round 50 points as starting credit.

\noindent The points you have generated in the individual rounds will be added together with your starting credit.

\noindent At the end of the study, the points are converted into real money. Here, 1 point is converted into 9 cents.
